\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2023-03-09 doc/USER_MANUAL/02_getting_started.tex
updates doc

Note that we use CUBIT (now called Trelis) to create meshes of hexahedra, but other packages
can be used as well, for instance GiD from \url{http://gid.cimne.upc.es}
or Gmsh from \url{http://geuz.org/gmsh} \citep{GeRe09}. Even mesh
creation packages that generate tetrahedra, for instance TetGen from
\url{http://tetgen.berlios.de}, can be used because each tetrahedron
can then easily be decomposed into four hexahedra as shown in the
picture of the TetGen logo at \url{http://tetgen.berlios.de/figs/Delaunay-Voronoi-3D.gif};
while this approach does not generate hexahedra of optimal quality,
it can ease mesh creation in some situations and it has been shown
that the spectral-element method can very accurately handle distorted
mesh elements \citep{OlSe11}.\newline

@@

\begin{itemize}
\item[\textbullet] a good and short summary for the basic utilisation of Doxygen:

\url{http://www.softeng.rl.ac.uk/blog/2010/jan/30/callgraph-fortran-doxygen/},

@@

\url{http://www.stack.nl/~dimitri/doxygen/manual/diagrams.html},

@@

\url{http://www.stack.nl/~dimitri/doxygen/manual/config.html},

@@

\url{http://www.stack.nl/~dimitri/doxygen/manual/index.html}.

>>>>

Note that we use CUBIT (now called Trelis) to create meshes of hexahedra, but other packages
can be used as well, for instance GiD from \url{https://www.gidsimulation.com}
or Gmsh from \url{http://gmsh.info} \citep{GeRe09}. Even mesh
creation packages that generate tetrahedra, for instance TetGen from
\url{http://tetgen.berlios.de}, can be used because each tetrahedron
can then easily be decomposed into four hexahedra as shown in the
picture of the TetGen logo at \url{http://tetgen.berlios.de/figs/Delaunay-Voronoi-3D.gif};
while this approach does not generate hexahedra of optimal quality,
it can ease mesh creation in some situations and it has been shown
that the spectral-element method can very accurately handle distorted
mesh elements \citep{OlSe11}.\newline

@@

\begin{itemize}
\item[\textbullet] short summary for the basic utilisation of Doxygen:

\url{https://www.doxygen.nl/manual/starting.html},

@@

\url{https://www.doxygen.nl/manual/diagrams.html},

@@

\url{https://www.doxygen.nl/manual/config.html},

@@

\url{https://www.doxygen.nl/manual/index.html}.

### 2023-03-09 doc/USER_MANUAL/05_running_the_solver.tex
updates doc

For any particular earthquake, the \texttt{CMTSOLUTION} file that
represents the point source may be obtained directly from the Global
Centroid-Moment Tensor (CMT) web page \urlwithparentheses{www.globalcmt.org}.
It looks like the example shown in Fig. \ref{fig:CMTSOLUTION-file}.
\begin{figure}[htp]
\begin{centering}
\includegraphics[width=0.8\textwidth]{figures/Hollywood_CMT.jpg}
\par
\end{centering}
\caption{\texttt{CMTSOLUTION} file based on the
format from the Global CMT catalog. \textbf{M} is the moment tensor,
$M_{0}${\small {} }is the seismic moment, and $M_{w}$ is the moment
magnitude.}
\label{fig:CMTSOLUTION-file}
\end{figure}
%
The \texttt{CMTSOLUTION} file should be edited in the following way:
\begin{itemize}
\item Set the latitude or UTM $x$ coordinate, longitude or UTM $y$ coordinate, depth of the source (in km). Remark: In principle in the international CMTSOLUTION format in geophysics
the depth is given in kilometers; however for users in other fields (non-destructive testing, medical imaging, near-surface studies...) who may prefer to give the position of the source (rather than its depth from the surface), or for people who use \texttt{FORCESOLUTION} to describe the source rather than \texttt{CMTSOLUTION}, we provide an option called \texttt{USE\_SOURCES\_RECEIVERS\_Z} in the \texttt{DATA/Par\_file}, and if so that position is read from \texttt{CMTSOLUTION} in meters rather than kilometers (and again, it is then the true position in the mesh, not the depth). When option \texttt{USE\_SOURCES\_RECEIVERS\_Z} in the \texttt{DATA/Par\_file} is on, this remark applies to the position of the receivers as well.
\item Set the \texttt{time shift} parameter equal to $0.0$ (the solver
will not run otherwise.) The time shift parameter would simply apply
an overall time shift to the synthetics, something that can be done
in the post-processing (see Section \ref{sec:Process-data-and-syn}).
\item For point-source simulations (see finite sources, page \pageref{To-simulate-a}),
setting the source half-duration parameter \texttt{half duration} equal to zero corresponds to simulating a step source-time
function (Heaviside), i.e., to using a moment-rate function that is a delta function. If
\texttt{half duration} is not set to zero, the code will use a smooth (pseudo) Heaviside source-time function
with a corresponding Gaussian moment-rate function
(i.e., a signal with a shape similar to a `smoothed triangle', as
explained in \citet{KoTr02a} and shown in Fig~\ref{fig:gauss.vs.triangle})
with half-width \texttt{half duration}.

Often, it is preferable to run the solver with \texttt{half duration} set to zero and convolve
the resulting synthetic seismograms in post-processing after the run,
because this way it is easy to use a variety of source-time functions
(see Section \ref{sec:Process-data-and-syn}). \citet{KoTr02a} determined
that the noise generated in the simulation by using a step source
time function may be safely filtered out afterward based upon a convolution
with the desired source-time function and/or low-pass filtering. Use
the serial code \texttt{convolve\_source\_timefunction.f90} and the
script \texttt{convolve\_source\_timefunction.csh} for this purpose,
or alternatively use signal-processing software packages such as SAC
\urlwithparentheses{www.llnl.gov/sac}. Type
{\small
\begin{verbatim}
make xconvolve_source_timefunction
\end{verbatim}
}
to compile the code and then set the parameter \texttt{hdur} in \texttt{convolve\_source\_timefunction.csh}
to the desired half-duration.

>>>>

For any particular earthquake, the \texttt{CMTSOLUTION} file that
represents the point source may be obtained directly from the Global
Centroid-Moment Tensor (CMT) \href{www.globalcmt.org}{web page}.
It looks like the example shown in Fig. \ref{fig:CMTSOLUTION-file}.
\begin{figure}[htp]
\begin{centering}
\includegraphics[width=0.8\textwidth]{figures/Hollywood_CMT.jpg}
\par
\end{centering}
\caption{\texttt{CMTSOLUTION} file based on the
format from the Global CMT catalog. \textbf{M} is the moment tensor,
$M_{0}${\small {} }is the seismic moment, and $M_{w}$ is the moment
magnitude.}
\label{fig:CMTSOLUTION-file}
\end{figure}
%
The \texttt{CMTSOLUTION} file should be edited in the following way:
\begin{itemize}
\item Set the latitude or UTM $x$ coordinate, longitude or UTM $y$ coordinate, depth of the source (in km). Remark: In principle in the international CMTSOLUTION format in geophysics
the depth is given in kilometers; however for users in other fields (non-destructive testing, medical imaging, near-surface studies...) who may prefer to give the position of the source (rather than its depth from the surface), or for people who use \texttt{FORCESOLUTION} to describe the source rather than \texttt{CMTSOLUTION}, we provide an option called \texttt{USE\_SOURCES\_RECEIVERS\_Z} in the \texttt{DATA/Par\_file}, and if so that position is read from \texttt{CMTSOLUTION} in meters rather than kilometers (and again, it is then the true position in the mesh, not the depth). When option \texttt{USE\_SOURCES\_RECEIVERS\_Z} in the \texttt{DATA/Par\_file} is on, this remark applies to the position of the receivers as well.
\item Set the \texttt{time shift} parameter equal to $0.0$ (the solver
will not run otherwise.) The time shift parameter would simply apply
an overall time shift to the synthetics, something that can be done
in the post-processing (see Section \ref{sec:Process-data-and-syn}).
\item For point-source simulations (see finite sources, page \pageref{To-simulate-a}),
setting the source half-duration parameter \texttt{half duration} equal to zero corresponds to simulating a step source-time
function (Heaviside), i.e., to using a moment-rate function that is a delta function. If
\texttt{half duration} is not set to zero, the code will use a smooth (pseudo) Heaviside source-time function
with a corresponding Gaussian moment-rate function
(i.e., a signal with a shape similar to a `smoothed triangle', as
explained in \citet{KoTr02a} and shown in Fig~\ref{fig:gauss.vs.triangle})
with half-width \texttt{half duration}.

Often, it is preferable to run the solver with \texttt{half duration} set to zero and convolve
the resulting synthetic seismograms in post-processing after the run,
because this way it is easy to use a variety of source-time functions
(see Section \ref{sec:Process-data-and-syn}). \citet{KoTr02a} determined
that the noise generated in the simulation by using a step source
time function may be safely filtered out afterward based upon a convolution
with the desired source-time function and/or low-pass filtering. Use
the serial code \texttt{convolve\_source\_timefunction.f90} and the
script \texttt{convolve\_source\_timefunction.csh} for this purpose
(or alternatively use signal-processing software packages such as \href{https://seiscode.iris.washington.edu/projects/sac}{SAC}).
Type
{\small
\begin{verbatim}
make xconvolve_source_timefunction
\end{verbatim}
}
to compile the code and then set the parameter \texttt{hdur} in \texttt{convolve\_source\_timefunction.csh}
to the desired half-duration.

### 2023-03-09 doc/USER_MANUAL/11_graphics.tex
updates doc

In case you used the internal mesher \texttt{xmeshfem3D} to create
and partition your mesh, you can output mesh files in ABAQUS (.INP)
and DX (.dx) format to visualize them. For this, you must set either
the flag \texttt{CREATE\_DX\_FILES} or \texttt{CREATE\_ABAQUS\_FILES}
to \texttt{.true.} in the mesher's parameter file \texttt{Mesh\_Par\_file}
prior to running the mesher (see Chapter~\ref{cha:Running-the-Mesher-Meshfem3D}
for details). You can then use AVS \urlwithparentheses{www.avs.com}
or OpenDX \urlwithparentheses{www.opendx.org} to visualize the mesh
and MPI partition (slices).

@@

You have also the option to visualize the distributed databases produced
by \texttt{xgenerate\_databases} using Paraview \urlwithparentheses{www.paraview.org}.
For this, you must set the flag \texttt{SAVE\_MESH\_FILES} to \texttt{.true.}
in the main parameter file \texttt{DATA/Par\_file} (see Chapter~\ref{cha:Main-Parameter}
for details). This will create VTK files for each single partition.
You can then use Paraview \urlwithparentheses{www.paraview.org}
to visualized these partitions.\newline

@@

\end{description}
The \texttt{SPECFEM3D Cartesian} code is running in near real-time
to produce animations of southern California earthquakes via the web;
see Southern California ShakeMovie\textregistered{}\urlwithparentheses{www.shakemovie.caltech.edu}.

@@

Notice that this Perl script uses a program \texttt{mesh2vtu} in the \texttt{utils/Visualization/Paraview/mesh2vtu} directory, which further
uses the VTK \urlwithparentheses{http://www.vtk.org} run-time library for its execution. Therefore, make sure you have them properly set
in the script according to your system.\newline

@@

\item Notice that this Perl script uses a program \texttt{mesh2vtu} in the
\texttt{\small utils/Visualization/Paraview/mesh2vtu} directory, which further
uses the VTK \urlwithparentheses{http://www.vtk.org/} run-time library
for its execution. Therefore, make sure you have them properly set
in the script according to your system.
\end{enumerate}

@@

Finally, we can view the mesh in ParaView \urlwithparentheses{www.paraview.org}.
\begin{enumerate}
\item Open ParaView.
\item From the top menu, \textsf{File} $\rightarrow$\textsf{Open data},
select \texttt{file.vtu}, and click the \textsf{Accept} button.

\begin{itemize}
\item If the mesh file is of moderate size, it shows up on the screen; otherwise,
only the bounding box is shown.
\end{itemize}
\item Click \textsf{Display Tab} $\rightarrow$ \textsf{Display Style} $\rightarrow$
\textsf{Representation} and select \textsf{wireframe of surface} to
display it.
\item To create a cross-section of the volumetric mesh, choose \textsf{Filter}
$\rightarrow$ \textsf{cut}, and under \textsf{Parameters Tab}, choose
\textsf{Cut Function} $\rightarrow$ \textsf{plane}.
\item Fill in center and normal information given by the \texttt{global\_slice\_number.pl}
script (either from the standard output or from \texttt{normal\_plane.txt}
file).
\item To change the color scale, go to \textsf{Display Tab} $\rightarrow$
\textsf{Color} $\rightarrow$ \textsf{Edit Color Map} and reselect
lower and upper limits, or change the color scheme.
\item Now load in the source and receiver location file by \textsf{File}
$\rightarrow$ \textsf{Open data}, select \texttt{sr.vt}k, and click
the \textsf{Accept} button. Choose \textsf{Filter} $\rightarrow$
\textsf{Glyph}, and represent the points by `\textsf{spheres}'.
\item For more information about ParaView, see the ParaView Users Guide
\urlwithparentheses{www.paraview.org/files/v1.6/ParaViewUsersGuide.PDF}.
\end{enumerate}
\end{enumerate}
%
\begin{figure}[H]
\begin{centering}
\includegraphics[width=6in]{figures/3D-S-Kernel.jpg}
\par
\end{centering}
\caption{(a) Top Panel: Vertical source-receiver cross-section of the S-wave
finite-frequency sensitivity kernel $K_{\beta}$ for station GSC at
an epicentral distance of 176 km from the September 3, 2002, Yorba
Linda earthquake. Lower Panel: Vertical source-receiver cross-section
of the 3D S-wave speed model used for the spectral-element simulations
\citep{KoLiTrSuStSh04}. (b) The same as (a) but for station HEC at
an epicentral distance of 165 km \citep{LiTr06}.}
\label{figure:P-wave-speed-finite-frequency}
\end{figure}

>>>>

In case you used the internal mesher \texttt{xmeshfem3D} to create
and partition your mesh, you can output mesh files in ABAQUS (.INP)
and DX (.dx) format to visualize them. For this, you must set either
the flag \texttt{CREATE\_DX\_FILES} or \texttt{CREATE\_ABAQUS\_FILES}
to \texttt{.true.} in the mesher's parameter file \texttt{Mesh\_Par\_file}
prior to running the mesher (see Chapter~\ref{cha:Running-the-Mesher-Meshfem3D}
for details). You can then use \href{www.avs.com}{AVS}
or \href{www.opendx.org}{OpenDX} to visualize the mesh
and MPI partition (slices).

@@

You have also the option to visualize the distributed databases produced
by \texttt{xgenerate\_databases} using \href{www.paraview.org}{Paraview}.
For this, you must set the flag \texttt{SAVE\_MESH\_FILES} to \texttt{.true.}
in the main parameter file \texttt{DATA/Par\_file} (see Chapter~\ref{cha:Main-Parameter}
for details). This will create VTK files for each single partition.
You can then use \href{www.paraview.org}{Paraview}
to visualized these partitions.\newline

@@

\end{description}
The \texttt{SPECFEM3D Cartesian} code is running in near real-time
to produce animations of southern California earthquakes via the web;
see Southern California \href{www.shakemovie.caltech.edu}{ShakeMovie\textregistered{}}.

@@

Notice that this Perl script uses a program \texttt{mesh2vtu} in the \texttt{utils/Visualization/Paraview/mesh2vtu} directory, which further
uses the \href{http://www.vtk.org}{VTK} run-time library for its execution. Therefore, make sure you have them properly set
in the script according to your system.\newline

@@

\item Notice that this Perl script uses a program \texttt{mesh2vtu} in the
\texttt{\small utils/Visualization/Paraview/mesh2vtu} directory, which further
uses the \href{http://www.vtk.org/}{VTK} run-time library
for its execution. Therefore, make sure you have them properly set
in the script according to your system.
\end{enumerate}

@@

Finally, we can view the mesh in \href{www.paraview.org}{ParaView}.
\begin{enumerate}
\item Open ParaView.
\item From the top menu, \textsf{File} $\rightarrow$\textsf{Open data},
select \texttt{file.vtu}, and click the \textsf{Accept} button.

\begin{itemize}
\item If the mesh file is of moderate size, it shows up on the screen; otherwise,
only the bounding box is shown.
\end{itemize}
\item Click \textsf{Display Tab} $\rightarrow$ \textsf{Display Style} $\rightarrow$
\textsf{Representation} and select \textsf{wireframe of surface} to
display it.
\item To create a cross-section of the volumetric mesh, choose \textsf{Filter}
$\rightarrow$ \textsf{cut}, and under \textsf{Parameters Tab}, choose
\textsf{Cut Function} $\rightarrow$ \textsf{plane}.
\item Fill in center and normal information given by the \texttt{global\_slice\_number.pl}
script (either from the standard output or from \texttt{normal\_plane.txt}
file).
\item To change the color scale, go to \textsf{Display Tab} $\rightarrow$
\textsf{Color} $\rightarrow$ \textsf{Edit Color Map} and reselect
lower and upper limits, or change the color scheme.
\item Now load in the source and receiver location file by \textsf{File}
$\rightarrow$ \textsf{Open data}, select \texttt{sr.vt}k, and click
the \textsf{Accept} button. Choose \textsf{Filter} $\rightarrow$
\textsf{Glyph}, and represent the points by `\textsf{spheres}'.
\item For more information about ParaView, see the
\href{www.paraview.org/files/v1.6/ParaViewUsersGuide.PDF}{ParaView Users Guide}.
\end{enumerate}
\end{enumerate}
%
\begin{figure}[H]
\begin{centering}
\includegraphics[width=6in]{figures/3D-S-Kernel.jpg}
\par
\end{centering}
\caption{(a) Top Panel: Vertical source-receiver cross-section of the S-wave
finite-frequency sensitivity kernel $K_{\beta}$ for station GSC at
an epicentral distance of 176 km from the September 3, 2002, Yorba
Linda earthquake. Lower Panel: Vertical source-receiver cross-section
of the 3D S-wave speed model used for the spectral-element simulations
\citep{KoLiTrSuStSh04}. (b) The same as (a) but for station HEC at
an epicentral distance of 165 km \citep{LiTr06}.}
\label{figure:P-wave-speed-finite-frequency}
\end{figure}

### 2023-03-09 doc/USER_MANUAL/14_post_processing.tex
updates doc

The original data and synthetics have three components: vertical (BHZ
resp. BXZ), north (BHN resp. BXN) and east (BHE resp. BXE). However,
for most seismology applications, transverse and radial components
are also desirable. Therefore, we need to rotate the horizontal components
of both the data and the synthetics to the transverse and radial direction,
and \texttt{\small rotate.pl}{\small{} can be used to accomplish this:}{\small \par}
\begin{verbatim}
rotate.pl -l 0 -L 180 -d DATA/*.BHE.SAC.bp
rotate.pl -l 0 -L 180 SEM/*.BXE.semd.sac.bp
\end{verbatim}
where the first command performs rotation on the SAC data obtained
through Seismogram Transfer Program (STP) \urlwithparentheses{http://www.data.scec.org/STP/stp.html},
while the second command rotates the processed SEM synthetics.

>>>>

The original data and synthetics have three components: vertical (BHZ
resp. BXZ), north (BHN resp. BXN) and east (BHE resp. BXE). However,
for most seismology applications, transverse and radial components
are also desirable. Therefore, we need to rotate the horizontal components
of both the data and the synthetics to the transverse and radial direction,
and \texttt{\small rotate.pl}{\small{} can be used to accomplish this:}{\small \par}
\begin{verbatim}
rotate.pl -l 0 -L 180 -d DATA/*.BHE.SAC.bp
rotate.pl -l 0 -L 180 SEM/*.BXE.semd.sac.bp
\end{verbatim}
where the first command performs rotation on the SAC data obtained
through Seismogram Transfer Program (\href{http://www.data.scec.org/STP/stp.html}{STP}),
while the second command rotates the processed SEM synthetics.

### 2023-03-09 doc/USER_MANUAL/copyright_and_version.tex
updates doc

MPI v. 3.0, December 2014: many developers.
Convolutional PML, LDDRK time scheme, bulk attenuation support, simultaneous MPI runs,
ADIOS file I/O support, new seismogram names,
Deville routines for additional GLL degrees, tomography tools, unit/regression test framework,
improved CUDA GPUs performance, additonal GEOCUBIT support, better make compilation,
git versioning system. \newline

MPI v. 2.1, July 2012: Max Rietmann, Peter Messmer, Daniel Peter, Dimitri
Komatitsch, Joseph Charles, Zhinan Xie: support for CUDA GPUs, better
CFL stability for the Stacey absorbing conditions. \newline

MPI v. 2.0, November 2010: Dimitri Komatitsch, Nicolas Le Goff, Roland
Martin and Pieyre Le Loher, University of Pau, France, Daniel Peter,
Jeroen Tromp and the Princeton group of developers, Princeton University,
USA, and Emanuele Casarotti, INGV Roma, Italy: support for CUBIT meshes
decomposed by SCOTCH; much faster solver using Michel Deville's inlined
matrix products.\newline

MPI v. 1.4 Dimitri Komatitsch, University of Pau, Qinya Liu and others,
Caltech, September 2006: better adjoint and kernel calculations, faster
and better I/Os on very large systems, many small improvements and
bug fixes.\newline

MPI v. 1.3 Dimitri Komatitsch, University of Pau, and Qinya Liu, Caltech,
July 2005: serial version, regular mesh, adjoint and kernel calculations,
ParaView support.\newline

MPI v. 1.2 Min Chen and Dimitri Komatitsch, Caltech, July 2004: full
anisotropy, volume movie.\newline

MPI v. 1.1 Dimitri Komatitsch, Caltech, October 2002: Zhu's Moho map,
scaling of $V_{s}$ with depth, Hauksson's regional model, attenuation,
oceans, movies.\newline

MPI v. 1.0 Dimitri Komatitsch, Caltech, USA, May 2002: first MPI version
based on global code.\newline

>>>>

version 4.0, December 2022:
Rafael Almada, Jean-Paul Ampuero, Etienne Bachmann, Kangchen Bai, Stephen Beller, Jordan Bishop, Alexis Bottero,
Emanuele Casarotti, Clement Durochat, Rene Gassmoeller, Hom Nath Gharti, Leopold Grinberg, Aakash Gupta,
Foivos Karakostas, Dimitri Komatitsch, Qinya Liu, Geordie McBain, Ryan Modrak, Vadim Monteiller, Masaru Nagaso, Elif Oral,
Daniel Peter, Elliott Sales de Andrade,  James Smith, Carl Tape, Eduardo Valero Cano, Huihui Weng, Zhinan Xie:
various code improvements (fault solver, FK/DSM/AxiSEM coupling, gravity perturbations, energy integrals);
inverse problem module; parallel heuristic mesh decomposer; ADIOS2 file I/O support;
ASDF seismogram output; HIP GPU support.\newline

version 3.0, December 2014: many developers.
Convolutional PML, LDDRK time scheme, bulk attenuation support, simultaneous MPI runs,
ADIOS file I/O support, new seismogram names,
Deville routines for additional GLL degrees, tomography tools, unit/regression test framework,
improved CUDA GPUs performance, additonal GEOCUBIT support, better make compilation,
git versioning system. \newline

version 2.1, July 2012: Max Rietmann, Peter Messmer, Daniel Peter, Dimitri
Komatitsch, Joseph Charles, Zhinan Xie: support for CUDA GPUs, better
CFL stability for the Stacey absorbing conditions. \newline

version 2.0, November 2010: Dimitri Komatitsch, Nicolas Le Goff, Roland
Martin and Pieyre Le Loher, University of Pau, France, Daniel Peter,
Jeroen Tromp and the Princeton group of developers, Princeton University,
USA, and Emanuele Casarotti, INGV Roma, Italy: support for CUBIT meshes
decomposed by SCOTCH; much faster solver using Michel Deville's inlined
matrix products.\newline

version 1.4 Dimitri Komatitsch, University of Pau, Qinya Liu and others,
Caltech, September 2006: better adjoint and kernel calculations, faster
and better I/Os on very large systems, many small improvements and
bug fixes.\newline

version 1.3 Dimitri Komatitsch, University of Pau, and Qinya Liu, Caltech,
July 2005: serial version, regular mesh, adjoint and kernel calculations,
ParaView support.\newline

version 1.2 Min Chen and Dimitri Komatitsch, Caltech, July 2004: full
anisotropy, volume movie.\newline

version 1.1 Dimitri Komatitsch, Caltech, October 2002: Zhu's Moho map,
scaling of $V_{s}$ with depth, Hauksson's regional model, attenuation,
oceans, movies.\newline

version 1.0 (MPI) Dimitri Komatitsch, Caltech, USA, May 2002: first MPI version
based on global code.\newline
